Particular examples of planar integral point sets and their classification \footnote{ This work was carried out at Voronezh State University and supported by the Russian Science Foundation grant 19-11-00197. }

### 2025-11-17 AvdMomZvolA_examples/ips_examples.tex
[AMZA] Reincorporate the bibliography

\usepackage[backend=biber,style=gost-numeric,sorting=none]{biblatex}
\addbibresource{../common/notmy.bib}
\addbibresource{../common/my.bib}
\usepackage{../../../biblatex2bibitem/biblatex2bibitem}

\usepackage{hyperref}
%\usepackage{cite}

@@

\printbibliography
\printbibitembibliography

@@

>>>>

%\usepackage[backend=biber,style=gost-numeric,sorting=none]{biblatex}
%\addbibresource{../common/notmy.bib}
%\addbibresource{../common/my.bib}
%\usepackage{../../../biblatex2bibitem/biblatex2bibitem}

\usepackage{hyperref}
\usepackage{cite}

@@

@@

\begin{thebibliography}{99}
{}
\bibitem{anning1945integral}
\emph{Anning} \emph{N. H.}, \emph{Erdős} \emph{P.} Integral distances // Bulletin of
the American Mathematical Society. — 1945. — Vol. 51, no. 8. — Pp. 598–600. — DOI: \href
{https://doi.org/10.1090/S0002-9904-1945-08407-9} {\nolinkurl
{10.1090/S0002-9904-1945-08407-9}}.
{}
\bibitem{erdos1945integral}
\emph{Erdős} \emph{P.} Integral distances // Bulletin of the American Mathematical
Society. — 1945. — Vol. 51, no. 12. — P. 996. — DOI: \href
{https://doi.org/10.1090/S0002-9904-1945-08490-0} {\nolinkurl
{10.1090/S0002-9904-1945-08490-0}}.
{}
\bibitem{kemnitz1988punktmengen}
\emph{Kemnitz} \emph{A.} Punktmengen mit ganzzahligen Abständen. — 1988.
{}
\bibitem{kurz2005characteristic}
\emph{Kurz} \emph{S.} On the characteristic of integral point sets in {$\mathbb
{E}^m$} // Australasian Journal of Combinatorics. — 2006. — Vol. 36. — Pp. 241–248. —
arXiv: \href {http://arxiv.org/abs/math/0511704} {\nolinkurl {math/0511704}}.
{}
\bibitem{kurz2008minimum}
\emph{Kurz} \emph{S.}, \emph{Wassermann} \emph{A.} On the minimum diameter of
plane integral point sets // Ars Combinatoria. — 2011. — Vol. 101. — Pp. 265–287. — arXiv:
\href {http://arxiv.org/abs/0804.1307} {\nolinkurl {0804.1307}}.
{}
\bibitem{solymosi2003note}
\emph{Solymosi} \emph{J.} Note on integral distances // Discrete \& Computational
Geometry. — 2003. — Vol. 30, no. 2. — Pp. 337–342. — DOI: \href
{https://doi.org/10.1007/s00454-003-0014-7} {\nolinkurl {10.1007/s00454-003-0014-7}}.{}
\bibitem{avdeev-lushina2025australas}
\emph{Avdeev} \emph{N.}, \emph{Lushina} \emph{E.} On the characteristic and diameter
of planar integral point sets // Australasian Journal of Combinatorics. — (in press). — DOI:
\href {https://doi.org/10.48550/arXiv.2407.08121} {\nolinkurl
{10.48550/arXiv.2407.08121}}. — arXiv: \href {http://arxiv.org/abs/2407.08121} {\nolinkurl
{2407.08121}}. — URL: \url
{https://ui.adsabs.harvard.edu/abs/2024arXiv240708121A/abstract}.
{}
\bibitem{kreisel2008heptagon}
\emph{Kreisel} \emph{T.}, \emph{Kurz} \emph{S.} There are integral heptagons, no three
points on a line, no four on a circle // Discrete \& Computational Geometry. — 2008. —
Vol. 39, no. 4. — Pp. 786–790. — DOI: \href {https://doi.org/10.1007/s00454-007-9038-6}
{\nolinkurl {10.1007/s00454-007-9038-6}}.
{}
\bibitem{our-ped-2018}
\emph{Авдеев} \emph{Н. Н.} On integral point sets in special position // Некоторые
вопросы анализа, алгебры, геометрии и математического образования: материалы
международной молодежной научной школы «Актуальные направления математического
анализа и смежные вопросы». — 2018. — Vol. 8. — Pp. 5–6.
{}
\bibitem{our-pmm-2018}
\emph{Авдеев} \emph{Н. Н.} Об отыскании целоудалённых множеств специального
вида // Актуальные проблемы прикладной математики, информатики и механики -
сборник трудов Международной научной конференции. — Научно-исследовательские
публикации, 2018. — Pp. 492–498.
{}
\bibitem{our-vmmsh-2018-translit}
\emph{Avdeev} \emph{N. N.}, \emph{Semenov} \emph{E. M.} Integral point sets in the
plane and Euclidean space (Множества точек с целочисленными расстояниями на
плоскости и в евклидовом пространстве) // Matematicheskij forum (Itogi nauki. Yug
Rossii). — 2018. — Pp. 217–236.
{}
\bibitem{avdeev2019particular}
\emph{Avdeev} \emph{N. N.}, \emph{Zvolinsky} \emph{R. E.},
\emph{Momot} \emph{E. A.} On particular diameter bounds for integral point sets in higher
dimensions // Вестн. ВГУ. Серия: Физика. Математика. — 2025. — Vol. 1. — Pp. 62–77. —
arXiv: \href {http://arxiv.org/abs/1909.10386} {\nolinkurl {1909.10386}}. — URL: \url
{https://ui.adsabs.harvard.edu/abs/2019arXiv190910386A/abstract}.
{}
\bibitem{kurz2013constructing}
Constructing $7$-clusters / S. Kurz [et al.] // Serdica Journal of Computing. — 2014. — Vol. 8,
no. 1. — Pp. 47–70. — arXiv: \href {http://arxiv.org/abs/1312.2318} {\nolinkurl {1312.2318}}.
{}
\bibitem{antonov2008maximal}
\emph{Antonov} \emph{A. R.}, \emph{Kurz} \emph{S.} Maximal integral point sets over
{$\mathbb {Z}^2$} // International Journal of Computer Mathematics. — 2008. — Vol. 87,
no. 12. — Pp. 2653–2676. — DOI: \href {https://doi.org/10.1080/00207160902993636}
{\nolinkurl {10.1080/00207160902993636}}. — arXiv: \href {http://arxiv.org/abs/0804.1280}
{\nolinkurl {0804.1280}}.{}
\bibitem{solymosi2010question}
\emph{Solymosi} \emph{J.}, \emph{De Zeeuw} \emph{F.} On a question of Erdős and
Ulam // Discrete \& Computational Geometry. — 2010. — Vol. 43, no. 2. — Pp. 393–401. —
arXiv: \href {http://arxiv.org/abs/0806.3095} {\nolinkurl {0806.3095}}.
{}
\bibitem{our-mz-rus-translit}
\emph{Avdeev} \emph{N. N.}, \emph{Semenov} \emph{E. M.} On point sets in the plane
with integral distances (О множествах точек на плоскости с целочисленными
расстояниями) // Matematicheskie zametki. — 2016. — Vol. 100, no. 5. — Pp. 757–761.
\end{thebibliography}
